Centers and centralizers of higher enveloping algebras of Lie algebras

### 2020-09-10 draft.tex
spec seq

\begin{proof}
For $U \subset M \times \RR_{>0}$ the underlying graded vector space of $\bC_n(\fg)(U)$ is of the form
\[
{\rm Hom}^\bu\left(\Sym(\fg \otimes \Omega^\bu (U)[1]) \; , \; {\rm Sym}  \left(\fg \otimes \Omega^\bu_c(U) [2] \right) \right)  .
\]
Let $x^* \otimes \alpha$ denote an homorphism of the form $\fg \otimes \Omega (U) \to \Sym^0 = k$ and $y \otimes \beta$ denote a homomorphism $k = \Sym^0 \to \fg \otimes \Omega_c(U) [2]$. 
Then, the bracket involving the linear elements $x^* \otimes \alpha$ 
and $y \otimes \beta$ is defined by
\begin{align*}
\{x^* \otimes \alpha  , y \otimes \beta \} & = \<x^*, y\>_\fg \int_U \alpha \beta \\
\{x^* \otimes \alpha , x'^* \otimes \alpha' \} & = 0 \\
\{y \otimes \beta , y' \otimes \beta'\} & = 0 . 
\end{align*}
Here, $\<x^*, y\>_\fg$ denotes the linear pairing between $\fg$ and $\fg^*$ and $\int_U\alpha \beta$ denotes the linear pairing between compactly supported distributional differential forms and differential forms. \brian{how to say this now}
The bracket is extended to the entire symmetric algebra by using the graded Leibniz rule.
\end{proof}

@@

The pair $(\int_{\RR_{>0}} , \int_{\RR_{\geq 0}})$ is a quasi-isomorphisms of factorization sc-pairs. 
The compatibility of this quasi-isomorphism with Poisson brackets is a direct calculation. 
\end{proof}

@@

\brian{spectral sequence}

%\subsection{The bulk TFT}
%
%Let us place the locally constant factorization algebra model of the $\EE_n$-enveloping algebra $\bU_n (\fg) = \clieu(\fg \otimes \Omega_c)$ on the $n$-manifold $M$.
%This factorization algebra is equivalent to the pushforward of a factorization algebra $\Obs_{\rm BF}$ on the $(n+1)$-dimensional manifold $M \times \RR$ along the projection $\pi : M \times (0,1) \to M$ which we proceed to construct. 
%
%\begin{dfn}
%For an open set $V \subset M \times (0,1)$ let $\Obs^{\rm cl}_{\rm BF} (V)$ be the cochain complex 
%\[
%\Obs^{\rm cl}_{\rm BF} (V) = \clie \bigg(\fg \otimes \Omega (V) \; , \; \Sym \left(\fg \otimes \Omega_c(V) [2] \right) \bigg) .
%\]
%The assignment $V \mapsto \Obs^{\rm cl}_{\rm BF}(V)$ defines a locally constant factorization algebra on $M \times (0,1)$. 
%\end{dfn}
%
%We note that $\Obs_{\rm BF}^{\rm cl}$ is a factorization algebra with values in commutative dg algebras. 
%In fact, it is given by the ``classical observables" of a topological field theory on $M \times (0,1)$ known as ``topological BF theory". 
%
%We now consider the pushforward factorization algebra $\pi_* \Obs^{\rm cl}_{\rm BF}$ on $M$.
%Locally, on disks, we will see that it is quasi-isomorphic to a certain limit, or ``dequantization", of our model for the $\EE_n$-center of $\UU_n \fg$.
%Recall, this model is given by the factorization algebra on $M$:
%\begin{equation}\label{eqn:centerTFT}
%\bZ_n(\fg) = \clie\left(\fg \otimes \Omega \, , \, \clieu (\fg \otimes \Omega_c) \right) .
%\end{equation}
%
%The ``dequantization" is defined using the following filtration of this model.
%For any Lie algebra $\fh$, let $\clieu_{\leq k} (\fh)$ be the subcomplex of Chevalley--Eilenberg chains which is $\Sym^{\leq k} (\fh[1])$ as an underlying graded vector space. 
%
%\begin{dfn}
%Introduce the filtration on the factorization algebra on $M$ in (\ref{eqn:centerTFT}) by 
%\[
%F^k \bZ_n(\fg) = \clie \bigg(\fg \otimes \Omega \; , \; \clieu_{\leq k} (\fg \otimes \Omega_c) \bigg) .
%\]
%\end{dfn}
%
%This is a filtration of factorization algebras on $M$. 
%The associated graded factorization algebra is
%\[
%{\rm Gr} \; \bZ_n(\fg) \; = \; \clie \bigg(\fg \otimes \Omega \; , \; \Sym \left(\fg \otimes \Omega_c [1] \right) \bigg) .
%\]
%Notice this is similar to the model $\EE_n$-center except we have turned off the Chevalley--Eilenberg differential on chains. 
%
% \begin{lmm}
%There is a quasi-isomorphism of commutative factorization algebras on $M$:
%\[
%\pi_* \Obs^{\rm cl}_{\rm BF} \; \xto{\simeq} \; {\rm Gr} \; \bZ_n(\fg) .
%\]
%\end{lmm}
%
%In fact, we will show that this quasi-isomorphism is a deformation retraction. 
%
%\begin{proof}
%To exhibit this quasi-isomorphism, we introduce the following cochain maps.
%For an open set $U \subset M$ let
%\[
%\int_\RR : \Omega_c(U \times \RR) \to \Omega_c (U) [1] 
%\] 
%be the map which integrates a compactly supported form on $U \times \RR$ along $\RR$. 
%This map is a quasi-isomorphism for any $U $ and admits the following explicit retract. 
%Let $\phi$ be a fixed compactly supported function on $\RR$ of mass $1$ and define
%\[
%r_\phi : \Omega_c(U) [1] \to \Omega_c (U \times \RR)
%\]
%by $r_\phi (\alpha) = \alpha \wedge \phi \, \d t$. 
%\end{proof}

%\begin{lmm}
%Consider the locally constant factorization algebra $\cF_{\rm bulk}$ on $M \times \RR$ which assigns to an open set $U \subset M \times \RR$
%\[
%\cF_{\rm bulk} = \clie \left(\fg \otimes \Omega (U) \; , \; \clieu (\fg \otimes \Omega_c (U)[1]) \right) .
%\]
%Then, 
%\end{lmm}
%
%\begin{proof}
%For $V \subset M$, the integration of compactly supported de Rham forms along $\RR$ 
%\[
%\fg \otimes \Omega_c (\pi^{-1} (V)) = \fg \otimes \Omega_c (V \times \RR) \xto{\int_{\RR}} \fg \otimes \Omega_c (V) [-1] .
%\]
%is a quasi-isomorphism. 
%
%\end{proof}

>>>>

\begin{proof}
For $U \subset M \times \RR_{>0}$ the underlying graded vector space of $\bC_n(\fg)(U)$ is of the form
\[
{\rm Hom}^\bu\left(\Sym(\fg \otimes \Omega^\bu (U)[1]) \; , \; {\rm Sym}  \left(\fg \otimes \Omega^\bu_c(U) [2] \right) \right)  .
\]
Let $x^* \otimes \alpha$ denote an homomorphism of the form $\fg \otimes \Omega (U) \to \Sym^0 = k$ and $y \otimes \beta$ denote a homomorphism $k = \Sym^0 \to \fg \otimes \Omega_c(U) [2]$. 
The bracket between these linear elements $x^* \otimes \alpha$ 
and $y \otimes \beta$ is defined by
\begin{align*}
\{x^* \otimes \alpha  , y \otimes \beta \} & = \<x^*, y\>_\fg \int_U \alpha \beta \\
\{x^* \otimes \alpha , x'^* \otimes \alpha' \} & = 0 \\
\{y \otimes \beta , y' \otimes \beta'\} & = 0 . 
\end{align*}
Here, $\<x^*, y\>_\fg$ denotes the linear pairing between $\fg$ and $\fg^*$ and $\int_U\alpha \beta$ denotes the linear pairing between compactly supported distributional differential forms and differential forms. \brian{how to say this now}
The bracket is extended to the entire symmetric algebra by using the graded Leibniz rule.
\end{proof}

@@

The pair of maps $(\int_{\RR_{>0}} , \int_{\RR_{\geq 0}})$ is a quasi-isomorphism of factorization sc-pairs. 
An explicit and direct calculation verifies that this quasi-isomorphism respects the Poisson brackets. 
\end{proof}

@@

We conclude by describing a useful application of this work back in algebraic topology.
The factorization sc-pair $(\bZ_n(\fg), \bU_n \fg)$ makes it quick and convenient to compute factorization homology over an $n$-dimensional manifold,
but that model is not amenable to computations over $n+1$-dimensional manifolds with boundary,
because $\bZ_n(\fg)$ is not explicitly described as a factorization algebra on $n+1$-dimensional manifolds.
Our work in this section does provide, however, an explicit description of~$\Gr {\frak Z}_n(\fg)$. 
Thus, we have access to the beginning of a spectral sequence.

\begin{prp}
Let $M$ be an $n+1$-dimensional manifold with boundary $\partial M$. 
As $(\frak{Z}_n(\fg), \UU_n \fg)$ form a filtered algebra over the Swiss cheese operad, 
there is a spectral sequence
\[
\int_{(M,\partial M)} (\Gr \frak{Z}_n(\fg), \Gr \UU_n \fg) \Longrightarrow \int_{(M,\partial M)} (\frak{Z}_n(\fg), \UU_n \fg).
\]
\end{prp}
